Manuscript Figures for Genome Biology

### 2018-10-09 manuscript_figures/manuscript_figures.Rmd
Consistent subtitle labels

# regexp to construct master data table separating case study datasets, methods
# and covariates
obj.names <- str_split(resfile, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[3]]))
inform <-  ifelse(grepl("uninf", resfile), "uninf", "inf")
type <-  ifelse(grepl("null", resfile), "null", "de")
size <-  ifelse(grepl("10", resfile), "10", "5")
mode <-  ifelse(grepl("II", resfile), "Bimodal effect Size", "Unimodal Effect Size")
pi0 <-  ifelse(grepl("H", resfile), "7.5% Non-null", "30% Non-null")
strength <- ifelse(grepl("W", resfile), "Weakly informative", "Strongly informative")
strength <- ifelse(grepl("uninf", resfile), "Uninformative", strength)
aseq <- seq(0.01, 0.10, by = 0.01)

>>>>

# regexp to construct master data table separating case study datasets, methods
# and covariates
obj.names <- str_split(resfile, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[3]]))
inform <-  ifelse(grepl("uninf", resfile), "uninf", "inf")
type <-  ifelse(grepl("null", resfile), "null", "de")
size <-  ifelse(grepl("10", resfile), "10", "5")
mode <-  ifelse(grepl("II", resfile), "Bimodal effect size", "Unimodal effect size")
pi0 <-  ifelse(grepl("H", resfile), "7.5% Non-null", "30% Non-null")
strength <- ifelse(grepl("W", resfile), "Weakly informative", "Strongly informative")
strength <- ifelse(grepl("uninf", resfile), "Uninformative", strength)
aseq <- seq(0.01, 0.10, by = 0.01)
